Towards a Formally Verified EVM in Production Environment

### 2020-04-25 COORDINATION2020/paper2.tex
paper6 update

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{verbatim}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{url}
\begin{document}
%
\title{Towards a Formally Verified EVM in Production Environment}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Xiyue Zhang\inst{1} \and
Yi Li\inst{1} \and
Meng Sun\inst{1}
}
%
% \authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{School of Mathematical Sciences, Peking University
\\
\email{\{xiyuezhang, liyi\_math, sunm\}@pku.edu.cn}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Among dozens of decentralized computing platforms, Ethe\-reum attracts widespread attention for its native support of smart contracts by means of a virtual machine called EVM. Programs can be developed in various front-end languages. For example, Solidity can be deployed to the blockchain in the form of compiled EVM opcodes. However, such flexibility leads to critical safety challenges. In this paper, we formally define the behavior of EVM in Why3, a platform for deductive program verification, which facilitates the verification of different properties. Furthermore, the extracted implementation in OCaml can be directly integrated into the production environment and tested against the standard test suite. The combination of proofs and testing in our framework serves as a powerful analysis basis for EVM and smart contracts.

@@

\section{Preliminary}\label{Sec: Pre}
\subsection{Why3}
Why3\cite{filliatre2013why3} is a tool for deductive program verification. It provides a standard library of logical theories, such as integer and real arithmetic, and basic programming data structures, such as arrays and queues. WhyML is the programming and specification language of Why3. The specification language is used to write program annotations and background logical theories, which serves as a common format for proof goals. Ghost code is also supported in WhyML, which serves to facilitate verification without affecting the final result of a program.

@@

Smart contracts are essentially programs deployed on the Ethereum blockchain used to conduct transactions or perform specific actions. Any user can create a contract by posting a transaction to the blockchain. The program code of the contract is fixed after deployment and it will be invoked whenever it receives a transaction. 
\section{EVM Framework}\label{Sec: Framework}
\subsection{Methodology of EVM Framework}
This framework can be considered as an experiment in a methodology that combines verification and testing for developing secure EVM implementations, and also as a tool for verifying smart contracts after compiling into bytecodes. Figure TOREF outlines the whole framework for developing a formally verified EVM in production environment.
\subsection{EVM in Why3}
According to the Ethereum project yellow paper\cite{wood2014ethereum}, we translated EVM into Why3, which provides a programming and specification language WhyML. Based on the EVM definitions, Why3 further generates verification conditions according to the property specification, and allows the users to split the goals into different subgoals and prove each subgoal through different Satisfiability Modulo Theories (SMT) solvers. In cases when the automatic SMT slovers cannot deal with, users can resort to interactive theorem proves based on the files generated by Why3.

As have been mentioned before, EVM is a simple stack-based machine. The memory model of EVM is a word-addressed byte array, which is volatile. The storage model of EVM is a non-volatile word-addressed word array. The perspective we see the execution process of a sequence of opcodes (instructions), which could be complied from a smart contract, is as a state transition process and it finally leads to a series of changes in the stack, memory and etc.

\subsubsection{Type Definition}
Based on the needs of type requirements of Ethereum, such as that the machine word of EVM is 256 bits and the address is 160 bits, we developed a series of type modules \texttt{UInt256}, \texttt{UInt160} and etc. to ease the representation of the corresponding types in Ethereum. Why3 also supports type alias which makes the source code in WhyML more readable. 
Stack is defined as a list of elements whose type are \texttt{uint256}, aliased by \texttt{machword}. Memory is defined as a function that maps \texttt{machword} to an option type \texttt{option memory\_content}. The \texttt{memory\_content} is an enumeration type including \texttt{Item8} and \texttt{Item256} since the memory content could be accessed through 256-bit store and 8-bit store instructions. Storage is defined as a function that maps \texttt{machword} to \texttt{machword}. There are also other enumeration types defined to reflect the virtual machine status, the operation error, and a big view of the returned result which are \texttt{vmstatus}, \texttt{error} and \texttt{return\_type}. The record type \textt{machine\_state} represents the machine state whose components contain stack, memory, program counter, vmstatus, the instruction list and etc..

\subsubsection{Instruction Definition}
Inspired by the instruction formalization of EVM in Lem \cite{hirai2017defining}, we defined the instruction set in different groups, such as arithmetic operations, stack operations and etc., then integrated them into a final type definition. The final instruction type definition is presented as follows, which shows the different instruction groups:
\begin{verbatim}
type instruction =
  | Invalid byte
  | Arith arith_inst  
  | Sarith sign_arith_inst
  | Bits bits_inst
  | Info info_inst
  | Memory memory_inst
  | Storage storage_inst
  | Pc pc_inst
  | Stack stack_inst
  | Dup dup_inst
  | Swap swap_inst
  | Log log_inst
  | System system_inst
\end{verbatim}
The organization of the instruction group is a bit different from the yellow paper\cite{wood2014ethereum}. The comparison operations are contained in the arithmetic operations \texttt{Arith} and the comparison operations for signed arithmetic are contained in the signed arithmetic operations \texttt{Sarith}, respectively. The bitwise operations and \texttt{BYTE} operation are included in the bit-related instructions \texttt{Bits}. Almost all of the information related instructions including environmental and block information are defined in type \texttt{info\_inst}, except some \texttt{CALL} and \texttt{CODE} instructions like the \texttt{CALLDATACOPY}, \texttt{CODECOPY} and \texttt{CALLDATALOAD} which are closely related to memory and stack. Therefore, for the memory and stack instruction groups, some extra instructions are added to the original instruction subsets presented in the yellow paper. In case when there exists some instruction that is illegal, the instruction \texttt{Invalid} is included in the instruction type definition. The \texttt{STOP} operation and the system operations from the yellow paper except \texttt{Invalid} are contained in the \textit{System} instruction set. As for the remaining instruction groups, they are basically the same as the corresponding instruction subsets in \cite{wood2014ethereum}. 
\subsubsection{Interpreter Definition}
The function interpreter maps from some machine state to a new machine state, mainly in charge of formalizing the state transition result of different instructions.
In order to make the definition of interpreter more concise, we defined some auxiliary functions. For example, the following function is used to obtain the instruction which needs to be executed from the instruction list according to the program counter. 
\begin{verbatim}
let get_inst (mac_st: machine_state): option instruction =
  match mac_st.mac_pc, mac_st.mac_insts with 
  | pc, insts -> (nth pc insts) 
  end    
\end{verbatim}
Item pop and push operations are most commonly-used manipulations for the state transition of stack. The auxiliary functions \texttt{push\_stack} and \texttt{pop\_stack} are defined to control the stack change. For the formalization of \texttt{Swap} instructions, two recursive functions \texttt{fetch} and \texttt{drop} are defined to manipulate lists and one main function \texttt{swap\_stack} that implements the stack swap instruction is defined further based on these two functions.
With the pre-defined auxiliary functions, the definition of the interpreter function is essentially comprised of component update of the machine state with regard to concrete instructions.

\subsection{OCaml Extraction and Rust Connection}
We customizedly defined a series of drivers to extract from WhyML programs to Ocaml programs.

\section{Experiment and Analysis}\label{Sec: Experiment}
We have presented the formal implementation of EVM in Why3, based on which important properties can be verified through automatic and interactive theorem provers. We proceed to test our executable OCaml implementation extracted from WhyML against the standard test suite. 
\section{Related Work}\label{Sec: Related}0
The research interest of using blockchain technology has exploded since the inception  of Bitcoin. As the popularity of the second generation blockchain Ethereum grows, a series of security vulnerabilities has also appeared. Since EVM and smart contracts deal directly with the transactions of valuable cryptocurrency units between different parties, the security of contract programs and EVM implementations is of paramount importance. To address the security challenges, researchers resort to the techniques of formal methods and program analysis.

\begin{itemize}
    \item \textbf{Formalization Foundation of EVM} An executable formal semantics of EVM have been created in K framework by Everett et al. \cite{hildenbrandt2017kevm}.  Hirai \cite{hirai2017defining} proposed an EVM implementation in Lem, a language that can be compiled for a few interactive theorem provers, and further proved some safety properties of smart contracts in Isabelle/HOL. The \texttt{hevm} project\cite{hevm} is implemented in Haskell especially for unit testing and debugging smart contracts though the EVM implementation is not completed yet. Besides the above formalizations of EVM, there are also implementations of EVM in Ruby\cite{cryptape}, Javascript\cite{vmjs}, Go\cite{vmgo} and etc.
    \item \textbf{Verification of Smart Contracts} Sergey et al. \cite{sergey2017concurrent} provides a new perspective between smart contracts and concurrent objects, based on which existing tools and insights for understanding, debugging and verifying concurrent objects can be used on smart contract behaviors. \cite{luu2016making} pointed out several new security problems and proposed a way to enhance the operational semantics of Ethereum to make smart contracts less vulnerable. Due to the difficulty of correcting the semantics of Ethereum, Luu et al.\cite{luu2016making} also implements a symbolic execution tool \texttt{OYENTE} to find security bugs. A framework to analyze and verify both the runtime safety and the functional correctness of Solidity contracts in F* was presented in \cite{bhargavan2016formal}.
\end{itemize}

@@

\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
%%%justified by the macro package automatically.} 
\label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{amscd}
\usepackage{amssymb}
\usepackage{epsf}
\usepackage{graphicx}
%\usepackage{times}
\usepackage{stmaryrd}
\usepackage{latexsym}
\usepackage{mathrsfs}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{fancyvrb}
\usepackage{fancybox}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{color}
\usepackage{tikz}
\usepackage{reotex}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{varwidth}
\usepackage{tabularx}
\usepackage{verbatim}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{url}
\begin{document}
%
\title{Towards a Formally Verified EVM in Production Environment}
\titlerunning{Towards a Formally Verified EVM in Production Environment}

%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Xiyue Zhang\inst{1} \and
Yi Li\inst{1} \and
Meng Sun\inst{1}
}
\authorrunning{X.~Zhang, Y.~Li and M.~Sun}
%
% \authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{School of Mathematical Sciences, Peking University
\\
\email{\{xiyuezhang, liyi\_math, sunm\}@pku.edu.cn}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Among dozens of decentralized computing platforms, Ethe\-reum attracts widespread attention for its native support of smart contracts by means of a virtual machine called EVM. Programs can be developed in various front-end languages. For example, Solidity can be deployed to the blockchain in the form of compiled EVM opcodes. However, such flexibility leads to critical safety challenges. In this paper, we formally define the behavior of EVM in Why3, a platform for deductive program verification, which facilitates the verification of different properties. Furthermore, the extracted implementation in OCaml can be directly integrated into the production environment and tested against the standard test suite. The combination of proofs and testing in our framework serves as a powerful analysis basis for EVM and smart contracts.

@@

\section{Preliminary}\label{Sec: Pre}
\subsection{Why3}
Why3~\cite{filliatre2013why3} is a tool for deductive program verification. It provides a standard library of logical theories, such as integer and real arithmetic, and basic programming data structures, such as arrays and queues. WhyML is the programming and specification language of Why3. The specification language is used to write program annotations and background logical theories, which serves as a common format for proof goals. Ghost code is also supported in WhyML, which serves to facilitate verification without affecting the final result of a program.

@@

Smart contracts are essentially programs deployed on the Ethereum blockchain used to conduct transactions or perform specific actions. Any user can create a contract by posting a transaction to the blockchain. The program code of the contract is fixed after deployment and it will be invoked whenever it receives a transaction.

\section{EVM Framework}\label{Sec: Framework}
%\subsection{Methodology of EVM Framework}
In this section, we demonstrate the EVM framework in detail. The main idea of the framework is to combine verification and testing towards developing secure EVM implementations.
It also provides the potential to verify smart contracts at the bytecode level.  This framework is mainly comprised of two parts: EVM specification in Why3 and experimental testing based on OCaml Extraction and Rust connection. This approach leverages on the formal methods and engineering, allowing us to perform both rigorous verification and efficient testing for EVM implementations and further smart contracts.

\subsection{EVM in Why3}
The first phase of the framework is to define a formal specification of EVM in Why3 and provide a platform for rigorous verification.  
We develop the EVM specification, following the Ethereum project yellow paper~\cite{wood2014ethereum}. More specifically, the EVM implementation is translated into WhyML, the programming and specification language of Why3. Towards the verification, verification conditions can be further generated through Why3, based on the EVM and property specification. The verification goals will then be split into a set of subgoals or directly be proved through the supported Satisfiability Modulo Theories (SMT) solvers. In cases when the automatic SMT slovers cannot deal with, users can resort to interactive theorem proves based on the files generated by Why3.

EVM is essentially a simple stack-based machine. The memory model of EVM is a word-addressed byte array, which is volatile. The storage model of EVM is a non-volatile word-addressed word array. The above three components form the infrastructure of EVM. Based on the formalization of the infrastructure, the most important is to capture the execution result of the EVM instructions. The perspective from which we deal with the execution process of a sequence of opcodes (instructions) is as a state transition process. This process starts with a initial state and leads to a series of changes in the stack, memory and etc. The formalization of base infrastructure and the instruction set are specified through \textit{Type Definition} and \textit{Instruction Definition}, respectively. \textit{Interpreter Definition} provides the specification of the interpreter and auxiliary functions.

\subsubsection{Type Definition}\label{sec:type}

To formalize the infrastructure of EVM, we first need to provide the formalization of some commonly-used types in EVM, such as the types of machine word and the address in EVM. Hence, we developed a series of type modules \texttt{UInt256}, \texttt{UInt160} and etc. to ease the representation of corresponding types in EVM. We also use type alias supported by Why3 to make the basic formalization more readable and consistent with the original definition.

To this end, the components of the base infrastructure can be specified. Stack is defined as a list of elements whose type is \texttt{uint256}, aliased by \texttt{machine word}. Memory is defined as a function that maps \texttt{machine word} to an option type \texttt{option memory\_content}. Since the memory content could be accessed through 256-bit store and 8-bit store instructions, \texttt{memory\_content} is defined as an enumeration type including \texttt{Item8} and \texttt{Item256}. Similarly, Storage is defined as a function that maps \texttt{machine word} to \texttt{machine word}. To reflect the implicit change of the machine state, we defined more miscellaneous types. For example, we use \texttt{vmstatus}, \texttt{error} and \texttt{return\_type} to capture the virtual machine status, the operation error, and the view of the returned result. The record type \texttt{machine\_state} is defined to represent the overall machine state which consists of stack, memory, program counter, vmstatus, the instruction list and etc.

\subsubsection{Instruction Definition}\label{sec:instruction}
The infrastructure has been built to specify the state of the virtual machine. Here we present the formal specification of the action set, i.e., the instruction set. Inspired by the instruction formalization in Lem~\cite{hirai2017defining}, we defined the instruction set in multiple groups, such as arithmetic operations, stack operations and etc., then integrated them into a summarized type definition \texttt{instruction}. The definition of \texttt{instruction} is presented as follows, where different subsets of instructions are wrapped up to form the complete specification.
\begin{verbatim}
type instruction =
  | Invalid byte
  | Arith arith_inst  
  | Sarith sign_arith_inst
  | Bits bits_inst
  | Info info_inst
  | Memory memory_inst
  | Storage storage_inst
  | Pc pc_inst
  | Stack stack_inst
  | Dup dup_inst
  | Swap swap_inst
  | Log log_inst
  | System system_inst
\end{verbatim}

The organization of the instruction category is a bit different from the yellow paper~\cite{wood2014ethereum}. The comparison operations are grouped in the arithmetic operation set \texttt{Arith}; and the comparison operations for signed arithmetic are included in the signed arithmetic operation set \texttt{Sarith}. The bitwise operations and operation \texttt{BYTE} are categorized into the bit-related instruction group \texttt{Bits}. The information related instructions including environmental and block information ones are defined in type \texttt{info\_inst}, except \texttt{CALL} and \texttt{CODE} instructions, such as \texttt{CALLDATACOPY}, \texttt{CODECOPY}, \texttt{CALLDATALOAD} and etc. These instructions are more closely related to memory and stack status. Therefore, extra instructions but closely-related ones are added to the original memory and stack instruction groups presented in the yellow paper. In case when some illegal command occurs, the instruction \texttt{Invalid} is included in the \texttt{instruction} definition. The \texttt{STOP} operation and the system operations from the yellow paper are defined in the \texttt{System} instruction set. The specification of the remaining instruction groups are basically the same as the corresponding instruction subsets in \cite{wood2014ethereum}.

\subsubsection{Interpreter Definition}\label{sec:interpreter}
The specification of \texttt{interpreter} formalizes the state transition result of different instructions. For a specific instruction, the interpreter determines the resultant machine status developing from the current status.
To make the definition of the interpreter more concise and compact, we defined some auxiliary functions. For example, the following function is used to obtain the next instruction to be executed. It is obtained from the instruction list following the program counter. 
\begin{verbatim}
let get_inst (mac_st: machine_state): option instruction =
  match mac_st.mac_pc, mac_st.mac_insts with 
  | pc, insts -> (nth pc insts) 
  end    
\end{verbatim}

Pop and push operations are most commonly-used manipulations for the state transition of stack. Auxiliary functions \texttt{push\_stack} and \texttt{pop\_stack} are defined to control the change of stack status. For capturing the status transition result of \texttt{Swap} instructions, recursive functions \texttt{fetch} and \texttt{drop} are defined to support more direct manipulation on lists. Function \texttt{swap\_stack} is defined further for state transition of swap instructions.
With the pre-defined auxiliary functions, the definition of the interpreter function is essentially comprised of machine status update with regard to concrete instructions.

\subsection{Experimental Testing}
We customizedly defined a series of drivers to extract WhyML programs into Ocaml programs.

\section{Experiment and Analysis}\label{Sec: Experiment}
We have presented the formal implementation of EVM in Why3, based on which important properties can be verified through automatic and interactive theorem provers. We proceed to test our executable OCaml implementation extracted from WhyML against the standard test suite.

\section{Related Work}\label{Sec: Related}
Research interest of blockchain technology has exploded since the inception  of Bitcoin. As the popularity of the second generation of blockchain, Ethereum, grows, a series of security vulnerabilities have also appeared. Since EVM and smart contracts deal directly with the transactions of valuable cryptocurrency units among multiple parties, the security of smart contract programs and EVM implementations is of paramount importance. To address the security challenges, researchers resorted to the techniques of formal methods and program analysis.

\begin{itemize}
    \item \textbf{Formalization Foundation of EVM} An executable formal semantics of EVM has been created in K framework by Everett et al.~\cite{hildenbrandt2017kevm}. Hirai~\cite{hirai2017defining} proposed an EVM implementation in Lem, a language that can be compiled for a few interactive theorem provers. Further, safety properties of smart contracts can be proved in proof assistants like Isabelle/HOL. The \texttt{hevm} project~\cite{hevm} is implemented in Haskell for unit testing and debugging smart contracts, though the EVM implementation is not completed yet. Besides the above formalizations of EVM, there are also implementations of EVM in Javascript~\cite{vmjs}, Go~\cite{vmgo}, Ruby~\cite{cryptape} and etc.
    \item \textbf{Verification of Smart Contracts} Sergey et al.~\cite{sergey2017concurrent} provided a new perspective between smart contracts and concurrent objects, based on which existing tools and insights for understanding, debugging and verifying concurrent objects can be used on smart contract behaviors. In \cite{luu2016making}, several new security problems were pointed out and a way to enhance the operational semantics of Ethereum was proposed to make smart contracts less vulnerable. Due to the difficulty of correcting the semantics of Ethereum, Luu et al.~\cite{luu2016making} also implemented a symbolic execution tool \texttt{OYENTE} to find security bugs. A framework to analyze and verify both the runtime safety and the functional correctness of Solidity contracts in F* was presented in \cite{bhargavan2016formal}.
\end{itemize}

@@

### 2020-04-25 COORDINATION2020/paper3.tex
paper6 update

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{amscd}
\usepackage{amssymb}
\usepackage{epsf}
\usepackage{graphicx}
%\usepackage{times}
\usepackage{stmaryrd}
\usepackage{latexsym}
\usepackage{mathrsfs}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{fancyvrb}
\usepackage{fancybox}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{color}
\usepackage{tikz}
\usepackage{reotex}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{varwidth}
\usepackage{tabularx}
\usepackage{verbatim}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{url}
\begin{document}
%
\title{Towards a Formally Verified EVM in Production Environment}
\titlerunning{Towards a Formally Verified EVM in Production Environment}

%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Xiyue Zhang\inst{1} \and
Yi Li\inst{1} \and
Meng Sun\inst{1}
}
\authorrunning{X.~Zhang, Y.~Li and M.~Sun}
%
% \authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{School of Mathematical Sciences, Peking University
\\
\email{\{xiyuezhang, liyi\_math, sunm\}@pku.edu.cn}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Among dozens of decentralized computing platforms, Ethe\-reum attracts widespread attention for its native support of smart contracts by means of a virtual machine called EVM. Programs can be developed in various front-end languages. For example, Solidity can be deployed to the blockchain in the form of compiled EVM opcodes. However, such flexibility leads to critical safety challenges. In this paper, we formally define the behavior of EVM in Why3, a platform for deductive program verification, which facilitates the verification of different properties. Furthermore, the extracted implementation in OCaml can be directly integrated into the production environment and tested against the standard test suite. The combination of proofs and testing in our framework serves as a powerful analysis basis for EVM and smart contracts.

@@

To this end, the components of the base infrastructure can be specified. Stack is defined as a list of elements whose type is \texttt{uint256}, aliased by \texttt{machine word}. Memory is defined as a function that maps \texttt{machine word} to an option type \texttt{option memory\_content}. Since the memory content could be accessed through 256-bit store and 8-bit store instructions, \texttt{memory\_content} is defined as an enumeration type including \texttt{Item8} and \texttt{Item256}. Similarly, Storage is defined as a function that maps \texttt{machine word} to \texttt{machine word}. To reflect the implicit change of the machine state, we defined more miscellaneous types. For example, we use \texttt{vmstatus}, \texttt{error} and \texttt{return\_type} to capture the virtual machine status, the operation error, and the view of the returned result. The record type \texttt{machine\_state} is defined to represent the overall machine state which consists of stack, memory, program counter, vmstatus, the instruction list and etc.

@@

The organization of the instruction category is a bit different from the yellow paper~\cite{wood2014ethereum}. The comparison operations are grouped in the arithmetic operation set \texttt{Arith}; and the comparison operations for signed arithmetic are included in the signed arithmetic operation set \texttt{Sarith}. The bitwise operations and operation \texttt{BYTE} are categorized into the bit-related instruction group \texttt{Bits}. The information related instructions including environmental and block information ones are defined in type \texttt{info\_inst}, except \texttt{CALL} and \texttt{CODE} instructions, such as \texttt{CALLDATACOPY}, \texttt{CODECOPY}, \texttt{CALLDATALOAD} and etc. These instructions are more closely related to memory and stack status. Therefore, extra instructions but closely-related ones are added to the original memory and stack instruction groups presented in the yellow paper. In case when some illegal command occurs, the instruction \texttt{Invalid} is included in the \texttt{instruction} definition. The \texttt{STOP} operation and the system operations from the yellow paper are defined in the \texttt{System} instruction set. The specification of the remaining instruction groups are basically the same as the corresponding instruction subsets in \cite{wood2014ethereum}.

@@

\subsection{Experimental Testing}
We customizedly defined a series of drivers to extract WhyML programs into Ocaml programs.

\section{Experiment and Analysis}\label{Sec: Experiment}
We have presented the formal implementation of EVM in Why3, based on which important properties can be verified through automatic and interactive theorem provers. We proceed to test our executable OCaml implementation extracted from WhyML against the standard test suite.

\section{Related Work}\label{Sec: Related}
Research interest of blockchain technology has exploded since the inception  of Bitcoin. As the popularity of the second generation of blockchain, Ethereum, grows, a series of security vulnerabilities have also appeared. Since EVM and smart contracts deal directly with the transactions of valuable cryptocurrency units among multiple parties, the security of smart contract programs and EVM implementations is of paramount importance. To address the security challenges, researchers resorted to the techniques of formal methods and program analysis.

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{verbatim}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{url}
\begin{document}
%
\title{Towards a Formally Verified EVM in Production Environment}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Xiyue Zhang\inst{1} \and
Yi Li\inst{1} \and
Meng Sun\inst{1}
}
%
% \authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{School of Mathematical Sciences, Peking University
\\
\email{\{xiyuezhang, liyi\_math, sunm\}@pku.edu.cn}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Among dozens of decentralized computing platforms, Ethereum attracts widespread attention for its native support of smart contracts by means of a virtual machine called EVM. Programs written in various front-end languages, Solidity, for example, can be deployed to the blockchain in form of compiled EVM opcodes. However, such flexibility also leads to safety challenges. In this paper, we formally define the behavior of EVM in Why3, a platform for deductive program verification, which facilitates the verification of different properties. Furthermore, the extracted implementation in OCaml can be directly integrated into the production environment and tested against the standard test suite. The combination of proofs and testing in our framework serves as a powerful analysis basis for EVM and smart contracts.

@@

To this end, the components of the base infrastructure can be specified. Stack is defined as a list of elements whose type is \texttt{uint256}, aliased by \texttt{machine word}. Memory is defined as a function that maps \texttt{machine word} to an option type \texttt{option memory\_content}. Since the memory content could be accessed through 256-bit store and 8-bit store instructions, \texttt{memory\_content} is defined as an enumeration type including \texttt{Item8} and \texttt{Item256}. Similarly, Storage is defined as a function that maps \texttt{machine word} to \texttt{machine word}. To reflect the implicit change of the machine state, we defined more miscellaneous types. For example, we use \texttt{vmstatus}, \texttt{error} and \texttt{return\_type} to capture the virtual machine status, the operation error, and the view of the returned result. The record type \textt{machine\_state} is defined to represent the overall machine state which consists of stack, memory, program counter, vmstatus, the instruction list and etc.

@@

The organization of the instruction category is a bit different from the yellow paper~\cite{wood2014ethereum}. The comparison operations are grouped in the arithmetic operation set \texttt{Arith}; and the comparison operations for signed arithmetic are included in the signed arithmetic operation set \texttt{Sarith}. The bitwise operations and operation \texttt{BYTE} are categorized into the bit-related instruction group \texttt{Bits}. The information related instructions including environmental and block information ones are defined in type \texttt{info\_inst}, except \texttt{CALL} and \texttt{CODE} instructions, such as \texttt{CALLDATACOPY}, \texttt{CODECOPY}, \texttt{CALLDATALOAD} and etc. These instructions are more closely related to memory and stack status. Therefore, extra instructions but closely-related ones are added to the original memory and stack instruction groups presented in the yellow paper. In case when some illegal command occurs, the instruction \texttt{Invalid} is included in the \textt{instruction} definition. The \texttt{STOP} operation and the system operations from the yellow paper are defined in the \texttt{System} instruction set. The specification of the remaining instruction groups are basically the same as the corresponding instruction subsets in \cite{wood2014ethereum}.

@@

\subsection{Running EVM in Production Environment}
%We customizedly defined a series of drivers to %extract WhyML programs into Ocaml programs. 
In this section, we introduce the second phase of the framework: deploy the verified EVM, encoded in Why3, in production environments. The deployment is essentially based on a co-compilation framework between OCaml and Rust.

OCaml is a functional programming language where the programs can be compiled either to OCaml bytecode or executable binaries. In the latter case, a runtime library is attached to handle various non-functional features like memory management. Through the \texttt{Callback} module, OCaml allows us to register a set of callback functions which can be used as an interface in static or dynamic linking. 
So we first defined a series of customized drivers to extract WhyML programs into Ocaml programs. After the extraction, the OCaml implementation of EVM is then encapsulated and exposed as a static linked library. This library can be further called by the EVM host in Rust.

The framework provides the interaction mechanism between Rust, the productive programming language, and Why3 the formal specification language. By gluing them together, verified models can be directly executed in production environments for further testing.

\section{Related Work}\label{Sec: Related}
Research interest of blockchain technology has exploded since the inception  of Bitcoin. As the popularity of the second generation of blockchain, Ethereum, grows, a series of security vulnerabilities have also appeared. Since EVM and smart contracts deal directly with the transactions of valuable c
ryptocurrency units among multiple parties, the security of smart contract programs and EVM implementations is of paramount importance. To address the security challenges, researchers resorted to the techniques of formal methods and program analysis.
